Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/Virgo Network

### 2013-08-16 doc/paper.tex
adding new pdfs

In Table \ref{ciTableIntrinsic}, we list the 65\% fractional credible
intervals for the mass parameters.  We find that the component masses
for equal mass systems can be isolated to between 6\% and 9\%
fractional uncertainty at the 65\% credible interval.  This value
drops to less than 2\% for the components of the unequal mass systems.
Again, this neglects the effects of spin which can substantially
increase these values.

@@

In Table \ref{ciTableExtrinsic}, we list the averaged 65\% confidence
intervals for distance and inclination.  Notice that the uncertainties
on distance can be extreme, from tens to hundreds of Mpc.  When
discussing the inclination angle, we elected to use $|\cos(\iota)|$,
as this maps the occasional bimodal structure into a single PDF, and
observing a compact merger at $\iota$ and $\iota + \pi/2$ should yield
identical physics.
%Since $|\cos(\iota)|$ maps the bi-modal structure in the inclination PDFs seen in Figure \ref{distIotaPDF} to a single
%mode, the uncertainties in $\iota$ will sufficiently small \carl{[QUANTIFY]} to provide coincident information on
%GRB beaming angles.

@@

\begin{table*}[t!]
\centering
\caption{Mean 65\% and 90\% credible intervals of extrinsic parameters for
  each of the four systems considered.  As expected, there exists a
  substantial improvement in the sky localization capabilities of the
  four-detector HLVI configuration over the three-detector HLV
  configuration.  Note that the solid-angle sky-location confidence
  intervals, $\Delta\Omega$, are calculated directly on the 2D sphere,
  not by combining the $\alpha$ and $\delta$ uncertainties.}

>>>>

In Table \ref{ciTableIntrinsic}, we list the 65\% and 90\% fractional credible
intervals for the mass parameters.  We find that the component masses
for equal mass systems can be isolated to between 6\% and 9\%
fractional uncertainty at the 65\% credible interval.  This value
drops to less than 2\% for the components of the unequal mass systems.
Again, this neglects the effects of spin which can substantially
increase these values.

@@

In Table \ref{ciTableExtrinsic}, we list the averaged 65\% and 90\% credible
intervals for distance and inclination.  Notice that the uncertainties
on distance can be extreme, from tens to hundreds of Mpc.  When
discussing the inclination angle, we elected to use $|\cos(\iota)|$,
as this maps the occasional bimodal structure into a single PDF, and
observing a compact merger at $\iota$ and $\iota + \pi/2$ should yield
identical physics.
%Since $|\cos(\iota)|$ maps the bi-modal structure in the inclination PDFs seen in Figure \ref{distIotaPDF} to a single
%mode, the uncertainties in $\iota$ will sufficiently small \carl{[QUANTIFY]} to provide coincident information on
%GRB beaming angles.

@@

\begin{table*}[t!]
\centering
\caption{Mean 65\% and 90\% credible intervals of extrinsic parameters for
  each of the four systems considered.  As expected, there exists a
  substantial improvement in the sky localization capabilities of the
  four-detector HLVI configuration over the three-detector HLV
  configuration.  Note that the solid-angle sky-location credible
  intervals, $\Delta\Omega$, are calculated directly on the 2D sphere,
  not by combining the $\alpha$ and $\delta$ uncertainties.}
